The Shape and Color of Politics

### 2023-09-27 chapter_2/src/slides/slides.qmd
a slight tweak to the slides and updating gitignore

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
---

@@

@@

@@

- Recruited 1,000 participants from Prolific
- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
- MouseView.js

@@

- Do these associations have systematic influences on campaign strategy?

- Collect around 1,000 yard signs from House elections
  - 2016-2024
- Measuring the colors used on a yard sign:
  - Use a machine learning Python Library, `OpenCV`, that reads images and classifies their components.
    - Trained to classify each pixel in the image
    - Classifies it based on BGR value (reverse of RGB)
    - Looks for a range of values around the "Republican red" and "Democratic blue"

>>>>

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
  cache: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

### Borrowing concepts from social neuroscience and psychology

- Memories:
  -  are multi-dimensional encodings of previous experiences [@fazio_attitudes_2007]
    - e.g., remember giving your first job talk
      - the layout of the room
      - the colors of the chairs
      - what the room smelled like
      - what ambient sounds were there
      - how you felt
  - affectively laden [@fazio_attitudes_2007;@winkielman_emotion_2011; @kensinger_affective_2022]
  - easier retrieved when recent and/or shares multiple commonalities with current object

@@

- Do these associations have systematic influences on campaign strategy? (Study 1)
- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)

- Collect around 1,000 yard signs from House elections
  - 2016-2024
- Measuring the colors used on a yard sign:
  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
    - Trained to classify each pixel in the image
    - Classifies it based on BGR value (reverse of RGB)
    - Looks for a range of values around the "Republican red" and "Democratic blue"

@@

- Recruited 1,000 participants from Prolific
- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
- MouseView.js [@anwyl-irvine_mouseviewjs_2022]

@@
